An Online Visual Loop Closure Detection Method for Indoor Robotic Navigation

### 2014-12-01 latex-spie/article.tex
Change in abstract

\begin{abstract}
Visual loop closure detection problem is an active area especially for the indoor environments, where the global position information is missing and the localization information is highly dependent on odometry sensors. In this paper, we propose an enhanced loop closure method based on unsupervised visual landmark extraction with saliency detection technique. In contradistinction to the previous methods, our approach uses additional depth information. Saliency regions are used to refer to the certain distinctive areas on the image patches. They are also suitable to represent locations in a sparse manner.  In order to find out the similarity between two locations we use a straightforward function, that contains the detection confidences of the image and the landmark coordinates in 3D. Recognition of the previously visited and unvisited locations is also considered in the framework. Exemplary results and the practical implementation of the method are also given with the data gathered on the testbed with a depth camera (Kinect) mounted differential drive autonomous ground vehicle. Specifically, we adopt visual place recognition to close loops that is useful for the process of correctly identifying a previously visited location. The algorithm is tested in three different datasets which lighting conditions are different from each other. Additional depth information beside the actual image increases the detection rate especially in dark. 
\end{abstract}

>>>>

\begin{abstract}
Visual loop closure detection problem is an active research area for indoor environments, where the global position information is missing and the localization information is highly dependent on odometry sensors. In this paper, we propose an enhanced loop closure method based on unsupervised visual landmark extraction by means of quantized local Zernike moments. In contradistinction to the previous methods, our approach uses additional depth information to extract Zernike moments. Zernike transform is an effective tool for referring to the certain distinctive areas on the image patches. Therefore, it is a suitable method to represent locations in a sparse manner.  In order to find out the similarity between two locations, we propose a straightforward function that contains the detection confidences of the image and the landmark coordinates in 3D. Recognition of the previously visited and unvisited locations are also considered in the framework. Examplary results and the practical implementation case of the method are also given with the data gathered on the testbed using a depth camera (Kinect) mounted differential drive autonomous ground vehicle. The results are referred as a successful, high-fidelity online method for visual place recognition as well as to close navigation loops, which is a crucial information for the well known simultaneously localization and mapping(SLAM) problem. The algorithm is tested in three different datasets of different lighting conditions. Additional depth information beside the actual image increases the detection rate especially in dark. 
\end{abstract}
